Playing Atari with Keras and R

### 2018-07-13 article.Rmd
add one more phrase

---
title: "Playing Atari with Keras and R"
output: html_document
---

@@

>>>>

---
title: "Playing Atari with Keras and R"
author: "Daniel Falbel and Fernando Barscevicius"
output: html_document
---

@@

Reinforcement learning is being used to solve many problems in robotics, delivery management or in the finance sector.
